Supermassive Black Hole Dynamics: A Proposal for a New Class of X-Ray Sources

### 2019-09-18 paper.tex
Mostly enlarged figures, modified captions.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/stellar_to_halo_ratio.png}
\caption{Approximation of Figure 11 from \citet{2018AstL...44....8K}.  Purple dots shown is example of our rescaled stellar masses}
\label{fig:stellar1}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/"Summary Results All Galaxies".png}
\caption{Histogram of merged, ejected, and orbiting SMBHs at z=0.}
\label{fig:meosmbh}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/q_merger_fraction.png}
\caption{Fraction of mergers per BH mass ratio.  Each point represents the fraction of galaxy mergers that led to BH mergers for each BH merger ratio bin.  Note that a "bin" at each point is comprised of the mass ratio at that point up to, but not including, the next point on the x-axis.}
\label{fig:q_merge_fraction}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/time_to_merge.png}
\caption{Time required for BHs to merge with host SMBH}
\label{fig:time_to_merge}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/kicked_stats.png}
\caption{Histogram of kicked and not-kicked SMBHs at z=0.}
\label{fig:kicked_stats}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/"Final Radius v Mass of Orbiting BHs".png}
\caption{Final Radii of remaining orbital black holes at z=0}
\label{fig:mvr}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/"Lx of our Galaxies compared to Babyk data".png}
\caption{X-ray luminosity of gas in our galaxies, compared to those from \citet{2018ApJ...857...32B}.}
\label{fig:galgas1}
\end{center}
\end{figure}

@@

\begin{figure}[htp]
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/"radiative efficiency".png}
\caption{Radiative efficiency of Orbiting Black Holes at z=0}
\label{fig:rad_eff}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/"luminosities_final".png}
\caption{Kohei Ratios of Orbiting BHs at z=0}
\label{fig:loobhs}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/"Final Luminosities using Kohei factor".png}
\caption{Luminosity Distribution of Orbiting BHs at z=0}
\label{fig:ldobhs}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/stellar_to_halo_ratio.png}
\caption{Approximation of Figure 11 from \citet{2018AstL...44....8K}.  Purple dots shown is example of our rescaled stellar masses}
\label{fig:stellar1}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/"Summary Results All Galaxies".png}
\caption{Histogram of merged, ejected, and orbiting SMBHs at z=0 as a function of BH mass.}
\label{fig:meosmbh}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/q_merger_fraction.png}
\caption{Fraction of BHs that merge with the central BH as a function of the BH mass ratio.  Each point represents the fraction of galaxy mergers that led to BH mergers for each BH merger ratio bin.  Note that a "bin" at each point is comprised of the mass ratio at that point up to, but not including, the next point on the x-axis.}
\label{fig:q_merge_fraction}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/time_to_merge.png}
\caption{Time required for BHs to merge with host SMBH after galaxy merger.}
\label{fig:time_to_merge}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/kicked_stats.png}
\caption{Histogram of kicked and not-kicked SMBHs at z=0.}
\label{fig:kicked_stats}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/"Final Radius v Mass of Orbiting BHs".png}
\caption{Final Radii of remaining orbital black holes at z=0}
\label{fig:mvr}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/"Lx of our Galaxies compared to Babyk data".png}
\caption{X-ray luminosity of hot gas in our galaxies, compared to those from \citet{2018ApJ...857...32B}.}
\label{fig:galgas1}
\end{center}
\end{figure}

@@

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/"luminosities_final".png}
\caption{Luminosity of orbiting BHs at z=0 as per Inayoshi (2019).}
\label{fig:loobhs}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/"Final Luminosities using Kohei factor".png}
\caption{Xray Luminosity Distribution of Orbiting BHs at z=0.}
\label{fig:ldobhs}
\end{center}
\end{figure}
